Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
add new ASS fig

%\begin{figure}
%\begin{center}
%\begin{tikzpicture}
%\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
%\node[anchor=south west,inner sep=0] at (-0.36, 0) {\includegraphics[height=2cm,width=5cm]{feature_histogram.png}};
%\node (histlabel1) at (2.3, 0.01) {$\mathbf{S}\boldsymbol{x}(\gamma)$};
%\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (histlabel1);
%\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (-0.3, 2.5);
%\node at (0.8, -0.35) {(a)};
%\node (histlabel2) at (7.6, 0.01) {$\log \mathbf{S}\boldsymbol{x}(\gamma)$};
%\node[anchor=south west,inner sep=0] at (3.45, 0) {\includegraphics[height=2cm,width=3cm]{feature_histogram_logcompressed.png}};
%\draw[-{Latex[length=2mm]}] (3.2, 0.01) -- (histlabel2);
%\draw[-{Latex[length=2mm]}] (4.9, 0.01) -- (4.9, 2.5);
%\node at (4.9, -0.35) {(b)};
%\end{tikzpicture}
%\caption{
%\label{fig:histograms}
%Histogram of values taken by the first-order scattering coefficient $\mathbf{S}\boldsymbol{x}(\gamma)$, corresponding to a center acoustic frequency of $302\,\mathrm{Hz}$,
%(a) before and (b) after logarithmic compression.}
%\end{center}
%\end{figure}

>>>>

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node[anchor=south west,inner sep=0] at (-0.36, 0) {\includegraphics[height=2cm,width=5cm]{feature_histogram.png}};
\node (histlabel1) at (2.3, 0.01) {$\mathbf{S}\boldsymbol{x}(\gamma)$};
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (histlabel1);
\draw[-{Latex[length=2mm]}] (-0.3, 0.01) -- (-0.3, 2.5);
\node at (0.8, -0.35) {(a)};
\node (histlabel2) at (7.6, 0.01) {$\log \mathbf{S}\boldsymbol{x}(\gamma)$};
\node[anchor=south west,inner sep=0] at (3.45, 0) {\includegraphics[height=2cm,width=3cm]{feature_histogram_logcompressed.png}};
\draw[-{Latex[length=2mm]}] (3.2, 0.01) -- (histlabel2);
\draw[-{Latex[length=2mm]}] (4.9, 0.01) -- (4.9, 2.5);
\node at (4.9, -0.35) {(b)};
\end{tikzpicture}
\caption{
\label{fig:histograms}
Histogram of values taken by the first-order scattering coefficient $\mathbf{S}\boldsymbol{x}(\gamma)$, corresponding to a center acoustic frequency of $302\,\mathrm{Hz}$,
(a) before and (b) after logarithmic compression.}
\end{center}
\end{figure}
